---
header-includes:
  - \usepackage{float}
  - \floatplacement{figure}{H}
output:
  pdf_document:
    includes:
      in_header: header.tex
      before_body: title_page.tex
    toc: TRUE
    number_sections: TRUE
    fig_caption: TRUE
    keep_md: FALSE
    keep_tex: FALSE
    toc_depth: 2
params:
 filter_parameter: !r tibble::tibble
 selected_features: !r character
 loq_statistics: !r tibble::tibble
 trafo_parameter: !r tibble::tibble
 model_parameter: !r tibble::tibble
 model_quality: !r tibble::tibble
 model_statistics: !r tibble::tibble
 normalization_parameter: !r tibble::tibble
 missing_statistics: !r tibble::tibble
 outliers_statistics: !r tibble::tibble
 imputation_statistics: !r tibble::tibble
 validation: !r tibble::tibble
 analysis_parameter: !r tibble::tibble
---



```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")

```
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
```
```{r echo=FALSE, eval=TRUE, include=FALSE}
pagebreak <- function() {
  if(knitr::is_latex_output())
    return("\\newpage")
  else
    return('<div style="page-break-before: always;" />')
}
```


\newpage
# Data set
Analysis report of the data set loaded from the file `r params$analysis_parameter$fileName`. The data set comprises `r params$analysis_parameter$numberOfInstances` instances that are characterized by `r params$analysis_parameter$numberOfFeatures` features, from which `r params$analysis_parameter$numberOfMetaFeatures` are defined as meta-features. The features are further split into `r params$analysis_parameter$numberOfNumericFeatures` numeric features, and `r params$analysis_parameter$numberOfNonNumericFeatures` non numeric features. The data set is missing `r params$analysis_parameter$totalNumberOfMissings` values. The analysis was prepared on `r format(Sys.time(), '%d %B, %Y')`.

\newpage
# Filter {#test-label}
The data set was filtered using the parameters described in Table \ref{tab:filter}.
```{r filter, message = FALSE, echo=FALSE, eval=TRUE}
params$filter_parameter %>%
  knitr::kable(format="latex", caption = "User defined filter set.")%>%
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

The following features were selected:

```{r, results='asis', message = FALSE, echo=FALSE, eval=TRUE}
cat(paste("- ", params$selected_features), sep = "\n")
```

\newpage
# Limits of quantification
Missing values have been indicated as `r params$analysis_parameter$loq_na_handling`. The LLOQ substitute was defined as `r params$analysis_parameter$lloq_substitute`. The ULOQ substitute was defined as `r params$analysis_parameter$uloq_substitute`. The statistics of the LOQ detection procedure are listed in table \ref{tab:detect-loq}.
```{r detect-loq, message = FALSE, echo=FALSE, eval=TRUE, size="small"}
params$loq_statistics %>%
  knitr::kable(format="latex", caption = "Result of the LOQ detection analysis.")%>%
  kableExtra::kable_styling(latex_options = c("scale_down","HOLD_position"))
```

\newpage
# Data transformation
The transformation procedure was performed using the parameters listed in table \ref{tab:trafo-para}.
```{r trafo-para, message = FALSE, echo=FALSE, eval=TRUE}
params$trafo_parameter %>%
  knitr::kable(format="latex", caption = "User defined transformation parameter.")%>%
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

## Modeling
The transformed data are fitted to the model of a normal distribution (see eq. \ref{eq:normal}).
\begin{align}
p\left(x | \mu, \sigma \right) = \frac{1}{\sqrt{2\pi\sigma^{2}}}e^{-\left(\frac{\left(x-\mu \right)^2}{2\sigma^{2}} \right)}
\label{eq:normal}
\end{align}
Here, $\mu$ defines the expectation value, and $\sigma$ defines the standard deviation of the model. The likelihood $p\left(x | \mu, \sigma \right)$ was optimized on the transformed data regarding to the model parameters $\mu$ and $\sigma$ in order to determine the model parameters $\hat{\mu}$ and $\hat{\sigma}$ that maximize the likelihood $\hat{L} = p\left(x | \hat{\mu}, \hat{\sigma} \right)$.

The determined model parameters for the transformed data are listed in table \ref{tab:model-para}.
```{r model-para, message = FALSE, echo=FALSE, eval=TRUE}
params$model_parameter %>%
  knitr::kable(format="latex", caption = "Model parameter of transformed feature distributions.")%>%
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

## Quality ensurance of modeling procedure
The model quality is estimated on the Bayesian Information Criterion (BIC), the Akaike Information Criterion (AIC), and the Root Mean Squared Error (RMSE). The BIC is calculated as depicted in equation \ref{eq:bic}.
\begin{align}
\text{BIC} &= k\ln(n)-2\ln(\hat{L})
\label{eq:bic}
\end{align}
with:
\begin{itemize}
\item $k :=$ the number of parameters estimated by the model.
\item $n :=$ the number of instances in the feature.
\item $\hat{L} :=$ the maximum likelihood function of the model.
\end{itemize}

The AIC is calculated as depicted in equation \ref{eq:aic}.
\begin{align}
\text{AIC} &= 2k-2\ln(\hat{L})
\label{eq:aic}
\end{align}
with:
\begin{itemize}
\item $k :=$ the number of parameters estimated by the model.
\item $\hat{L} :=$ the maximum likelihood function of the model.
\end{itemize}


The RSME is calculated as depicted in equation \ref{eq:rmse}.
\begin{align}
\text{RMSE} &= \sqrt{\sum^{n}_{i}\frac{\left(\hat{x}_{i} - x_{i} \right)^{2}}{n}}
\label{eq:rmse}
\end{align}
with:
\begin{itemize}
\item $n :=$ the number of instances in the feature.
\item $i :=$ running parameter.
\item $x_{i} :=$ observed values.
\item $\hat{x}_{i} :=$ predicted vales.
\end{itemize}

The model quality is listed in table \ref{tab:model-qual}. 
```{r model-qual, message = FALSE, echo=FALSE, eval=TRUE}
params$model_quality %>%
  knitr::kable(format="latex", caption = "Model quality.")%>%
  kableExtra::kable_styling(latex_options = c("scale_down","HOLD_position"))
```

## Statistics of modeling procedure
The statistics of the modeling procedure are listed in table \ref{tab:model-stats}.
```{r model-stats, message = FALSE, echo=FALSE, eval=TRUE}
params$model_statistics %>%
  knitr::kable(format="latex", caption = "Statistics of modeling procedure.")%>%
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

\newpage
## Rescaling
The selected rescaling method was `r params$analysis_parameter$normalization_type`. The choices for rescaling are min-max scaling, mean scaling and a z transformation. The mathematical implementation of min-max scaling is described in equation \ref{eq:min-max-scaling}.
Min-max scaling
\begin{align}
x' &= \frac{x - \text{min}\left( x\right)}{\text{max}\left( x\right) - \text{min}\left( x\right)}
\label{eq:min-max-scaling}
\end{align}
with:
\begin{itemize}
\item $x :=$ observed values.
\item $\text{max}(x) :=$ maximum of $x$.
\item $\text{min}(x) :=$ minimum of $x$.
\end{itemize}

The mathematical implementation of mean scaling is described in equation \ref{eq:mean-scaling}.
\begin{align}
x' &= \frac{x - \overline{x}}{\text{max}\left( x\right) - \text{min}\left( x\right)}
\label{eq:mean-scaling}
\end{align}
with:
\begin{itemize}
\item $x :=$ observed values.
\item $\overline{x} :=$ average of $x$.
\item $\text{max}(x) :=$ maximum of $x$.
\item $\text{min}(x) :=$ minimum of $x$.
\end{itemize}

The mathematical implementation of the z-transformation is described in equation \ref{eq:z-transformation}.
\begin{align}
x' &= \frac{x - \overline{x}}{\sigma}
\label{eq:z-transformation}
\end{align}
with:
\begin{itemize}
\item $x :=$ observed values.
\item $\overline{x} :=$ average of $x$.
\item $\sigma :=$ standard deviation of $x$.
\end{itemize}
