---
header-includes:
  - \usepackage{float}
  - \floatplacement{figure}{H}
output:
  pdf_document:
    includes:
      in_header: header.tex
      before_body: title_page.tex
    toc: TRUE
    number_sections: TRUE
    fig_caption: TRUE
    keep_md: FALSE
    toc_depth: 2
params:
 trafo_parameter: !r tibble::tibble
 model_parameter: !r tibble::tibble
 model_quality: !r tibble::tibble
 model_statistics: !r tibble::tibble
 analysis_parameter: !r tibble::tibble
---



```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
```
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
```
```{r echo=FALSE, eval=TRUE, include=FALSE}
pagebreak <- function() {
  if(knitr::is_latex_output())
    return("\\newpage")
  else
    return('<div style="page-break-before: always;" />')
}
```


\newpage
# Data transformation
## Data transformation parameter
Information about the user-selected data transformation methods.
```{r, message = FALSE, echo=FALSE, eval=TRUE}

params$trafo_parameter %>%
  knitr::kable(caption = "The famous iris data set")
```

## Modeling
The transformed data are fitted to the model of a normal distribution (see eq. \@ref(eq:normal)).
$$
p\left(x | \mu, \sigma \right) = \frac{1}{\sqrt{2\pi\sigma^{2}}}e^{-\left(\frac{\left(x-\mu \right)^2}{2\sigma^{2}} \right)}
\label{eq:normal}
$$
Here, $\mu$ defines the expectation value, and $\mu$ defines the standard deviation of the model. The determined model parameters for the transformed data are listed below.

```{r, message = FALSE, echo=FALSE, eval=TRUE}

params$model_parameter %>%
  knitr::kable(caption = "Model parameter of transformed data (mu := $\\mu$, sigma := $\\sigma$).")
```



